Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 algorithm.tex
pass through regret proof

The algorithm achieving the claimed bounds of
Theorem~\ref{thm:main-overview} is fairly simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled, 
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way the algorithm ensures each arm is pulled often enough.

More precisely, the algorithm divides time into \emph{phases}
$s = 1, 2, 3, \ldots$.
Phase $s$ starts when each arm has been pulled at least $s$ times.
We indicate the start time of phase $s$ by $t_s$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:
\pfdelete{
We call time $t_{s}=\min_{t}\{\forall i, \NumPull{t}{i} \geq s\}$ the
\emph{starting point of the $s^{th}$ phase}.
We call the set of times $[t_{s}, t_{s+1})$ the
\emph{$n^{th}$ phase}.
}

@@

When multiple arms are payment-eligible, the algorithm picks one
uniformly at random to incentivize.
When the algorithm decides to incentivize an arm $i$,
it offers ``whatever it takes,'' i.e., offers a payment of
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
The maximum for \AgV is taken over the support of \AgentDist;
recall that we assumed this support to be compact.
The payment \Pay{t}{i} may appear unnecessarily high.
Indeed, we show in Section~\ref{sec:pi} that it suffices to
incentivize only a $1/\log(s)$ fraction of the agents.
\dkcomment{Given that we don't prove anything there, is ``show'' the
  right word?}
Here, we focus on the higher payments for simplicity of analysis.

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\FOR{time steps $t = 1, 2, 3, \ldots$}
\IF{$\NumPull{t}{i} \geq s$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF{there is a payment-eligible arm $i$}
\STATE Let $i$ be a uniformly random payment-eligible arm.
\STATE Offer payment
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
for pulling arm $i$
(and payment 0 for all other arms).
\ELSE
\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

The high-level idea of the proof of Theorem~\ref{thm:main-overview}
is the following.
Because the algorithm ensures that each arm is pulled
``frequently enough,''
the estimates \ArmEV{t}{i} become exponentially more accurate in the
phase number $s$.
Thus, the fraction of agents who misidentify their best arm decreases
exponentially as well.
Because for each arm, enough agents have a true preference for this
arm, once the arms' attribute vectors are learned well enough,
the algorithm will not need to incentivize any more,
resulting in a payment bound independent of $T$.
Similarly, the regret will decrease exponentially, and mostly accrue
due to agents close to the border \pfcomment{we could clarify what border} making mistakes in their arm choices.
The detailed analysis following this outline is somewhat subtle, though,
due to the dependencies between the agents' arm pulls and the
estimates which in turn are based on past arm pulls.
We begin with several technical lemmas that are used for both the
payment and regret bounds.

To capture the probability masses of problematic and non-problematic
agents \pfcomment{in another pass we could seek to clarify what we mean by being problematic in the context of the border statement above}, we define the following:
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
is the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
\pfcomment{We can check through the whole paper on whether we have $\AgV \sim \AgentDist$ in the subscript or just $\AgV \sim \AgentDist$.  I think we have only $\AgentDist$ in the problem description.}
The minimum probability mass of users who prefer their best arm
sufficiently strongly over their second-best arm is denoted by
$\ClearPref{\delta} = \min_{i}
\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
Notice that \AlmostTied{\delta} (being a measure of problematic
agents) is defined as a sum over all arms,
while  \ClearPref{\delta} (being a measure of non-problematic agents)
is defined as a minimum over arms.
Also notice that $\ClearPref{0} = \MinProb$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

@@

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
\end{align} 
\label{rst:budget}
\end{theorem}

\begin{theorem}
For any given $T$, the cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
is bounded above by 
\begin{align}
O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
\end{align}
\label{rst:regret}
\end{theorem}

@@

The key technical lemma captures the intuition that
the estimates of the arms' attribute vectors become
exponentially more accurate with increasing phases $s$.
That intuition is captured by the following lemma.

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$, renormalized to have standard deviation $1/2$.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
Specifically, we set $b = \frac{x^2}{16 \sigma^2}$,
and obtain that

@@

In the high-probability case
$|S_J| \leq
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$,
we first use that $\sqrt{\cdot}$ is sublinear to bound
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}
\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$ (here we use the fact $\sqrt{J}\leq J$).

Then, we use the following technical Lemma~\ref{lem:n0-inequality}
(whose proof is given in Appendix~\ref{lem:n0-inequality-proof}, and whose
precondition we verify momentarily) to bound the first term,
giving us an overall upper bound of
$|S_J| \leq \frac{J x}{2 \sigma}$.

\begin{lemma} \label{lem:n0-inequality}
For any $n \geq \LatePhase = \max (2, \frac{30 \sigma^3}{x^3})$, 
\begin{align*}
\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} & \leq \frac{n x}{4 \sigma}. 
\end{align*}
\end{lemma}

Substituting the definition of $S_J$ and canceling common terms,
the inequality implies that
$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
By the assumptions of the lemma,
the stopping time $\tau$ is such that almost surely, each arm --- and
in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau$.
Defining $J$ to be the number of times that $i$ has been pulled at
time $\tau$, we obtain that $J$ satisfies the precondition of
Lemma~\ref{lem:n0-inequality}.
Furthermore, with probability 1, $J$ will be finite, meaning that
\begin{align*}
& \Prob{S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}\\
= & \Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}.
\end{align*}

Finally, this choice of $J$ ensures that
$\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
and we have thus shown that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
The lemma now follows by a union bound over all \ARMNUM arms and $d$
attributes.
\end{extraproof}

Lemma~\ref{lem:round-prob} implies that errors from myopic play
decrease exponentially in the phase number $s$.

@@

Thus, for any phase $s \geq \EvenLaterPhase$
Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
the expected total number of arm incentivizations is at most
\begin{align*}
&\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \nonumber \\
=& O\left( \max\{\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) \nonumber  \\
=& O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}

@@

\begin{proof}
Regret can arise in two ways:
(1) an agent was incentivized to pull a suboptimal arm, or
(2) an agent myopically pulled a suboptimal arm.
By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
incentivizes agents at most 
$O\left( N\exp\left(\frac{2}{p}\right) \right)$
times in expectation, each time causing regret at most \MAXR,
for a total expected regret of at most
$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
For the rest of the proof, we focus on the regret incurred when agents
pull arms myopically and make mistakes.

We distinguish between agents incurring large regret
(which requires severe misestimates of arm locations;
such misestimated are exponentially unlikely to occur), 
and agents incurring small positive regret,
which requires these agents to be almost tied in their preference for
the best arm.
To be more precise, we will define (with hindsight) a phase-dependent
cutoff $g(s)$, and consider a regret exceeding $g(s)$ large.

We first consider agents \AgV incurring positive regret less than $g(s)$.
The second-best arm \Second{\AgV} of \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
By Lemma~\ref{lem:sdelta}, the total measure of such agents
is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
and each incurs regret at most $g(s)$.
Summing over all time steps, the expected total regret from such agents is at most
\begin{align}
&E\left[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)\right] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \label{equ:small_regret_bound}
\end{align}

To bound the regret incurred in time steps with large regret,
let the random variable $t_s$ be the final time step in phase $s$,
for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
For $t = \tau_{s}^{k}$, we know
\begin{align}
&\Prob{\text{incur regret exceeding g(s)}} \nonumber \\
\leq & \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}}.\nonumber 
\end{align}

Because the regret never exceeds \MAXR,
the expected (large) regret for the \Kth{k} time step of phase $s$
is bounded above by
$\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR$.
Summing over all time steps $t$, we get that the total regret from
large-regret steps is at most

\begin{align*}
\lefteqn{\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR}
\\ & =
\sum_{s = 1}^T 
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \Expect{\mbox{Length of phase } s}
\\ & \leq
\sum_{s = 1}^T 
 \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \ARMNUM \log(s),
\end{align*}
where the inequality was an application of Lemma~\ref{lem:phase-length}.
Adding all three terms,
the cumulative regret up to time $T$ is at most

\begin{align}
&O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)
\\
+ & \sum_{s = 1}^T 
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
  \cdot \ARMNUM \log(s),
+ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot N\log(s). \label{thm:equ}
\end{align}

The first line is independent of $T$, and we now choose
$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$
with the goal of minimizing the second line.
With this choice and same definition of $S_{s}$ as in the proof of Lemma~\ref{lem:round-prob}, 
\begin{align*}
&\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \\
\leq &\sum_{i,j}\Prob{|S_s|\geq 2\sqrt{\frac{2}{1.8}s\log(T)}} \\
\leq &\sum_{i,j}\Prob{|S_s|\geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}} \leq 24\ARMNUM d \cdot \exp(-2\log(T)),
\end{align*}
where the second to last inequality is because the following technical inequality, whose proof we include in Appendix~\ref{lem:n1-inequality-proof}.

\begin{lemma} \label{lem:n1-inequality}
For any $T \geq 2$ and $1 \leq n \leq T$, we have
\begin{align*}
2\sqrt{\frac{2}{1.8} n \log(T)}
& \geq \sqrt{0.6 n \log(\log_{1.1}(n)+1) + \frac{2}{1.8} n \log(T)}.
\end{align*}
\end{lemma}

Therefore, the second line becomes

\begin{align*}
\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d \log(s) \MAXR \exp\left(-2\log(T)\right)  +
          \frac{128\ARMNUM\Diam^2 d^2\sigma^2
          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{\log(s)}{s}}
\\ & \leq
24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.11 \ARMNUM \Diam^2 d^2\sigma^2
          \TieDensity(\log(T))^2(\log(T)+1)
  \\ & \leq
12 \ARMNUM^2 d R  + 71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
\end{align*}

Adding all terms gives an upper bound of $O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right) +O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ on the cumulative expected regret.

\end{proof}

\dkcomment{Edited up to here.}

>>>>

\dkcomment{Here and earlier, we are using a lot of displayed
  equations. We could inline some/many of them to save space.}

The algorithm achieving the claimed bounds of
Theorem~\ref{thm:main-overview} is fairly simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled, 
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way the algorithm ensures that each arm is pulled often enough.

More precisely, the algorithm divides time into \emph{phases}
$s = 1, 2, 3, \ldots$.
Phase $s$ starts when each arm has been pulled at least $s$ times.
We indicate the start time of phase $s$ by $t_s$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:

@@

When multiple arms are payment-eligible, the algorithm picks one
uniformly at random to incentivize.
\dkcomment{Is uniform randomness used anywhere? Does arbitrary work?}
When the algorithm decides to incentivize an arm $i$,
it offers ``whatever it takes,'' i.e., offers a payment of
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
The maximum for \AgV is taken over the support of \AgentDist;
recall that we assumed this support to be compact.
The payment \Pay{t}{i} may appear unnecessarily high.
Indeed, we show in Section~\ref{sec:pi} that it suffices to
incentivize only a $1/\log(s)$ fraction of the agents.
\dkcomment{Given that we don't prove anything there, is ``show'' the
  right word?}
Here, we focus on the higher payments for simplicity of analysis.

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\COMMENT{Each arm is pulled once initially ``for free''.}
\FOR{time steps $t = 1, 2, 3, \ldots$}
\IF{$\NumPull{t}{i} \geq \dkedit{s+1}$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF{there is a payment-eligible arm $i$}
\STATE Let $i$ be a uniformly random payment-eligible arm.
\dkcomment{Is uniform randomness used anywhere?}
\STATE Offer payment
$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
for pulling arm $i$
(and payment 0 for all other arms).
\ELSE
\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

\dkcomment{I had written ``exponentially'' in a few places here, but I
  don't think that was correct. The error only decreases as
  $\sqrt{s}$, while the probability of deviating beyond that error
  decreases exponentially.}
The high-level idea of the proof of Theorem~\ref{thm:main-overview}
is the following.
Because the algorithm ensures that each arm is pulled
``frequently enough,''
the estimates \ArmEV{t}{i} become gradually more accurate in the
phase number $s$.
Thus, the fraction of agents who misidentify their best arm decreases.
Because for each arm, enough agents have a true preference for this
arm, once the arms' attribute vectors are learned well enough,
the algorithm will not need to incentivize any more,
resulting in a payment bound independent of $T$.
Similarly, the regret will decrease, and mostly accrue
due to ``problematic'' agents who are nearly tied in their preferences
between their top two arm choices.
The detailed analysis following this outline is somewhat subtle, though,
due to the dependencies between the agents' arm pulls and the
estimates which in turn are based on past arm pulls.
We begin with several technical lemmas that are used for both the
payment and regret bounds.

To capture the probability masses of problematic agents,
we define
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
\pfcomment{We can check through the whole paper on whether we have
  $\AgV \sim \AgentDist$ in the subscript or just $\AgV \sim
  \AgentDist$.  I think we have only $\AgentDist$ in the problem
  description.}
\dkcomment{There must be a typo in Peter's comment.}
%The minimum probability mass of users who prefer their best arm
%sufficiently strongly over their second-best arm is denoted by
%$\ClearPref{\delta} = \min_{i}
%\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
%\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
%Notice that \AlmostTied{\delta} (being a measure of problematic
%agents) is defined as a sum over all arms,
%while  \ClearPref{\delta} (being a measure of non-problematic agents)
%is defined as a minimum over arms.
%Also notice that $\ClearPref{0} = \MinProb$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}
\dkcomment{We weren't using $p(\delta)$ anywhere, so I got rid
  of it.}

@@

\dkcomment{Depending on how we structure Section 3, we might
get rid of those theorems, and only consider them parts of Theorem 2
that we prove here.}

\begin{theorem}
The expected payment budget for
Algorithm~\ref{alg:basic-incentivizing} is bounded above by
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
\end{align} 
\label{rst:budget}
\end{theorem}

\begin{theorem}
For any given $T$, the expected cumulative regret for
Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
above by 
\begin{align}
O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
\end{align}
\label{rst:regret}
\end{theorem}

@@

The key technical lemma captures the intuition that
the estimates of the arms' attribute vectors become
more accurate with increasing phases $s$.
That intuition is captured by the following lemma.

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
By the assumptions of the lemma,
the stopping time $\tau$ is such that almost surely, each arm --- and
in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau$.
Define $J$ to be the number of times that $i$ has been pulled at
time $\tau$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$, renormalized to have standard deviation $1/2$.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
the stopping time $J$.
Specifically, we set $b = \frac{x^2}{16 \sigma^2}$,
and obtain that

@@

Because $J$ will be finite with probability 1, we can drop the
$J < \infty$ part of the event:
\begin{align*}
& \Prob{S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}\\
= & \Prob{J < \infty \mbox{ and } S_J \geq 
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
    \sigma^2}}}.
\end{align*}

In the high-probability case
$|S_J| \leq
\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$,
we first use that $\sqrt{\cdot}$ is sublinear to bound
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}
\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$
(here we use the fact $\sqrt{J} \leq J$).
Then, we will show momentarily that
$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$,
giving us an overall upper bound of
$|S_J| \leq \frac{J x}{2 \sigma}$.

Substituting the definition of $S_J$ and canceling common terms,
the inequality implies that
$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
The choice of $J$ ensures that
$\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
and we have thus shown that
$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
The lemma now follows by a union bound over all \ARMNUM arms and $d$
attributes.

It remains to show that
$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$.
By squaring the statement and rearranging, it is equivalent to show that
$\frac{J}{\log(\log_{1.1}(J)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
Because $J \geq \LatePhase \geq 2$,
a numerical calculation and derivative test shows that
$\frac{J}{\log(\log_{1.1}(J)+1)} \geq J^{2/3}$,
and because $J \geq \LatePhase \geq \frac{30 \sigma^3}{x^3}$,
we get that
$J^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
\end{extraproof}

Lemma~\ref{lem:round-prob} implies that the probability of making
large errors due to myopic play decreases exponentially in the phase
number $s$.

@@

Thus, for any phase $s \geq \EvenLaterPhase$,
Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
with probability at most
$24 \ARMNUM d \cdot \exp \left(
  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
\right)$.
Summing over all arms and phases $s$,
and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
the expected total number of arm incentivizations is at most
\begin{align*}
&\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \nonumber \\
=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) \nonumber  \\
=& O\left( N\exp\left(\frac{2}{p}\right) \right).
\end{align*}

@@

\begin{extraproof}{Theorem~\ref{rst:regret}}
Regret can arise in two ways:
(1) an agent was incentivized to pull a suboptimal arm, or
(2) an agent myopically pulled a suboptimal arm.
By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
incentivizes agents at most 
$O\left( N\exp\left(\frac{2}{p}\right) \right)$
times in expectation, each time causing regret at most \MAXR,
for a total expected regret of at most
$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
For the rest of the proof, we focus on the regret incurred when agents
pull arms myopically and make mistakes.

We distinguish between agents incurring large regret
(which requires severe misestimates of arm locations;
such misestimated are exponentially unlikely to occur), 
and agents incurring small positive regret,
which requires these agents to be almost tied in their preference for
the best arm.
To be more precise, we will define (with foresight) a phase-dependent
cutoff
$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
and consider a regret exceeding $g(s)$ large.

We first consider agents \AgV incurring positive regret less than $g(s)$.
The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
By Lemma~\ref{lem:sdelta}, the total measure of such agents
is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
and each incurs regret at most $g(s)$.
Summing over all time steps,
and using Lemma~\ref{lem:phase-length} to bound the number of time
steps in phase $s$, 
the expected total regret from such agents is at most
\begin{align}
\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{align}

To bound the regret incurred in time steps with large regret,
we use a proof nearly identical to that of
Lemma~\ref{lem:round-prob} and Corollary~\ref{cor:right-choice}.
The only reason we cannot directly apply them is that in order
to apply to arbitrary $x > 0$, we had to assume that
$\LatePhase \geq \frac{30 \sigma^3}{x^3}$, a bound we cannot afford here.
So here, we will choose a larger value of $x$, and in return
will only need to assume that $T \geq 2$.

Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
Exactly as in the proof of Corollary~\ref{cor:right-choice},
it is sufficient to show that with high probability,
$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \frac{g(s)}{2\Diam d}$
for all arms $i$ and attributes $j$.

The proof of this high-probability guarantee for the stopping time
$t = \tau_s^k$ is identical to the proof of
Lemma~\ref{lem:round-prob} with $x = \frac{g(s)}{2 \Diam d}$
until the step where we start bounding
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$.
At that point in the proof, we had shown that 
the probability of $|S_J|$ exceeding the preceding expression is at most
\begin{align*}
24 \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
  & = \frac{24}{T^2}.
\end{align*}

Substituting $J = s$ and $x = \frac{g(s)}{2 \Diam d}$, the upper bound is
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{2 \log T}{1.8 J}}$.
We claim that for $J \leq T$ and $T \geq 2$, we have
$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{2 \log T}{1.8 J}}
\leq 2 \sqrt{\frac{2}{1.8} s \log(T)}$.
Indeed, by squaring this inequality and canceling out common terms,
the claimed inequality is equivalent to
$\frac{50}{9} \log T \geq \log(\log_{1.1}(J) + 1)$.
Because $J \leq T$, it is sufficient to show that
$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,
which can be verified by numerical calculation for $T=2$ and a
derivative test.

With this upper bound of $|S_J| \leq 2 \sqrt{\frac{2}{1.8} s \log(T)}$,
we can substitute the definition of $S_J$ to obtain that
$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \frac{g(s)}{2\Diam d}$
in the high-probability event.
By a union bound over all arms $i$ and attributes $j$,
the probability of incurring regret exceeding $g(s)$ is at most
$\frac{24 \ARMNUM d}{T^2}$.

Using that the regret never exceeds \MAXR,
and applying Lemma~\ref{lem:phase-length},
the total expected regret from large-regret steps is at most

\begin{align*}
\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
  \Prob{\mbox{incur regret exceeding } g(s) \mbox{ at step } t} \cdot \MAXR
& \leq
 \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
\\ & \leq 12 \ARMNUM^2 d \MAXR.
\end{align*}

Adding all three types of regret terms,
and substituting that 
$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most

\begin{align*}
\lefteqn{
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
\\ & = 
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
\end{align*}
\end{extraproof}
